D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-17 cuttingroom.tex
Add footnote on Rust asms
Reported-by: Ralf Jung <post@ralfj.de>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

There are a number of ways to implement \co{std::observable()},
for example, a new \co{"mightnotreturn"} GCC asm clobber, a call to an empty
function that is invisible to the compiler, and a GCC goto asm that the
compiler cannot prove falls through.

>>>>

There are a number of ways to implement \co{std::observable()},
for example, a new \co{"mightnotreturn"} GCC asm clobber, a call to an empty
function that is invisible to the compiler, and a GCC goto asm that the
compiler cannot prove falls through.\footnote{
	Rust defines non-pure asms as potentially looping forever.
	\url{https://github.com/rust-lang/reference/pull/1442}}
